---
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: library_handmade.bib
csl: methods-in-ecology-and-evolution.csl
urlcolor: black
linkcolor: black
fontsize: 12pt
geometry: margin = 1.2in
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
---

---
nocite: | 
  @Example1999, @Example2000
...

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, warning = FALSE, message = FALSE)
```

\pagenumbering{gobble}

```{r child = 'titlepage.Rmd'}
```

\newpage

```{r child = 'declaration.Rmd'}
```

\newpage
\pagestyle{fancy}

\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\pagenumbering{roman}

\fancyhead[CO,CE]{Abstract}
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

```{r child = 'abstract.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Acknowledgements}
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

```{r child = 'acknowledgements.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Table of Contents}
\setcounter{tocdepth}{2}
\tableofcontents

\newpage
\pagenumbering{arabic}

\newpage
\fancyhead[CO,CE]{Introduction}

```{r child = 'chapter1.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Methods}

```{r child = 'chapter2.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Results}

```{r child = 'chapter3.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Discussion}

```{r child = 'chapter4.Rmd'}
```

\FloatBarrier

\newpage
\fancyhead[CO,CE]{List of Figures}
\listoffigures

\newpage
\fancyhead[CO,CE]{List of Tables}
\listoftables

\newpage
\fancyhead[CO,CE]{References}

# References